\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-07-09 paper/eccv2020CR/main.tex
Added eccv2020 camera-ready draft.

% INITIAL SUBMISSION - The following two lines are NOT commented
% CAMERA READY - Comment OUT the following two lines
\usepackage{ruler}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

@@

%\newcommand{\edit}[1]{\textcolor{red}{#1}}
\newcommand{\edit}[1]{#1}

@@

%\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient} % Replace with your title
\title{Disambiguating Monocular Depth Estimation with a Single Transient} % Replace with your title

% INITIAL SUBMISSION 
%\begin{comment}
\titlerunning{ECCV-20 submission ID \ECCVSubNumber} 
\authorrunning{ECCV-20 submission ID \ECCVSubNumber} 
\author{Anonymous ECCV submission}
\institute{Paper ID \ECCVSubNumber}
%\end{comment}
%******************

% CAMERA READY SUBMISSION
\begin{comment}
\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
\end{comment}
%******************
\maketitle

>>>>

% INITIAL SUBMISSION - The following two lines are NOT commented
% CAMERA READY - Comment OUT the following two lines
% \usepackage{ruler}
% \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

@@

\newcommand{\edit}[1]{\textcolor{red}{#1}}
% \newcommand{\edit}[1]{#1}

@@

\title{Disambiguating Monocular Depth Estimation with a Single Transient} % Replace with your title

% CAMERA READY SUBMISSION
% \begin{comment}
\titlerunning{Disambiguating Monocular Depth Estimation with a Single Transient}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mark Nishimura  \and
David B. Lindell \and
Chris Metzler \and
Gordon Wetzstein}
%
\authorrunning{M. Nishimura et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Stanford University, Stanford, CA \\
\email{\{markn1, lindell, cmetzler, gordon.wetzstein\}@stanford.edu}}
%******************
\maketitle

### 2020-07-09 paper/eccv2020CR/sections/discussion.tex
Added eccv2020 camera-ready draft.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\paragraph{Limitations}

The performance of our method is highly dependent on the accuracy of the initial
depth map of the MDE algorithm.
%Since our method relies on the monocular depth estimate, the accuracy of the output depth map also relies on the performance of the initial depth estimate.
Our results demonstrate that when the MDE technique produces a depth map
with good ordinal accuracy, where the ordering of object depths is roughly correct, the
depth estimate can be corrected to produce accurate absolute depth. However, if
the ordering of the initial depths is not correct, these errors will not be
corrected by our histogram matching procedure and may propagate to the final
output depth map.

\edit{In the optically diffused configuration, the laser
power is spread out over the entire scene. Accordingly, for distant scene points very
little light may return to the SPAD and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method is best suited
to short to medium-range scenes with a reasonable power budget for the diffused
illumination.} \edit{For example, assuming an indoor scene with
fluorescent bulbs and an ambient spectral irradiance of $I_A =
1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
diffuse scene at $R = 3$ m
and a field of view of $\theta = 40^\circ$ can be calculated as}
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation} 
\edit{giving $P_{\text{min}}=21$ mW. We note that this is significantly 
less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.}

\edit{Under these scene parameters, we can compute the total incident 
  flux on the detector per second (derived in~\cite{mcmanamon2012ladar}) as}
  \begin{equation}
    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta
  \end{equation}
  \edit{where $P_T$ is the illumination power in the visible region, $\rho$ is its
  albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to
  the object, and $\eta$ is the quantum efficiency of the detector. For a range of 
  values similar to those of our experiments (detailed in the supplement), we find that
  the ratio of photon detections to illumination pulses is roughly 4\%, or well within 
  low-flux regime where SPAD pileup is negligible~\cite{oconnortcspc}.
  We also empirically validate that our method works with a diffused setup and an output power of 
  approximately 25 mW without significant pileup effects as shown in Figure~\ref{fig:captured_diffuse_small} and detailed in the supplement.
  } \edit{However, even for operation in the high-flux regime, pileup can be mitigated  
    by reducing the amount of incident light, for example by reducing the aperture size or 
    using neutral density filters, or by using a pileup correction~\cite{Heide:2018,Rapp:2019}.}

  %\edit{Note
  % that this calculation involves only on the signal-to-background photon ratio,
  % which is independent of the actual number of counts recorded per exposure. In
  % other words, pileup and laser energy concerns may 
  % be addressed entirely independently. As for acquisition time, at a 10 MHz
  % pulse rate with
  % a 5\% photon detection rate, it takes just two seconds to acquire a million
  % photon events.}

% \edit{Furthermore, our system uses a SPAD and is therefore susceptible to pileup.
% Because the SPAD must be quenched before it can
% detect another photon, earlier photons
% from closer objects may systematically prevent detection of photons from further
% objects, causing strong distortion of the transient. Fortunately, at the expense of
% longer acquisition times, pileup can be mitigated
% to a large extent by operating in the low-flux regime
% where the number of photon events per second is controlled to be at most 5\% the
% number of laser pulses per second~\cite{oconnortcspc}. Finally, even in
% the high-flux regime, it is sometimes possible to correct pileup computationally~\cite{Heide:2018}.}

% \edit{While our prototype shows results for scanned/summed measurements, our scanning prototype operates in the low-flux regime,
% avoiding pileup. A hypothetical diffused SPAD prototype could also operate in
% this low-flux regime, which would yield identical measurement models and identical
% results. Figure~\ref{fig:hardware}(b)-(c) empirically shows that collecting and summing scanned
% measurements is nearly identical to capturing diffused measurements. ?!We show
% empirical comparisons between the two modes on a more complex scene in the supplement?!}

% \edit{Even if diffused and scanned/summed measurements are equivalent
%   computationally, they are not equivalent energetically.  This number is dependent on scene albedo, but all time-of-flight imaging
% systems share this dependency.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Future Work}
While our hardware prototype is large, future work could miniaturize this
system. Our algorithm or similar sensor fusion algorithms could
also be integrated into electronics that already contain the required hardware
components, for example, existing cell phones with single-pixel SPAD
proximity sensors and RGB cameras.

>>>>

The performance of our method is highly dependent on the accuracy of the initial
depth map of the MDE algorithm. Our results demonstrate that when the MDE
technique produces a depth map with good ordinal accuracy, where the ordering of
object depths is roughly correct, the depth estimate can be corrected to produce
accurate absolute depth. However, if the ordering of the initial depths is not
correct, these errors will not be corrected by our histogram matching procedure
and may propagate to the final output depth map.

In the optically diffused configuration, the laser
power is spread out over the entire scene. Accordingly, for distant scene points
very little light may return to the SPAD, \edit{ making reconstruction difficult (an analogous
  problem occurs with dark objects).} \edit{Thus, our method is best suited
  to short to medium-range scenes.}
\edit{CONSIDER MOVE THIS ENTIRE CALCULATION TO
SUPPLEMENT} For example, assuming an indoor scene with
fluorescent bulbs and an ambient spectral irradiance of $I_A =
1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of
5 for a diffuse scene at $R = 3$ m and a field of view of
$\theta = 40^\circ$\textdegree can be calculated as
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation}
giving $P_{\text{min}}=21$ mW. We note that this is significantly
less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.

Under these scene parameters, we can compute the total incident
flux on the detector per second (derived in~\cite{mcmanamon2012ladar}) as
\begin{equation}
  P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta
\end{equation}
where $P_T$ is the illumination power in the visible region, $\rho$ is its
albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to the
object, and $\eta$ is the quantum efficiency of the detector. For a range of
values similar to those of our experiments (detailed in the supplement), we find
that the ratio of photon detections to illumination pulses is roughly 4\%, or
well within low-flux regime where SPAD pileup is negligible~\cite{oconnortcspc}.
We also empirically validate that our method works with a diffused setup and
an output power of approximately 25 mW without significant pileup effects as
shown in Figure~\ref{fig:captured_diffuse_small} and detailed in the supplement.

\edit{We acknowledge that pileup in bright environments will ultimately limit
  the maximum range of our method. However, even when operating in the high-flux
  regime, pileup can be mitigated by reducing the amount of incident light, for
  example by reducing the aperture size or using neutral density filters, or by
  using pileup correction~\cite{Heide:2018,Rapp:2019}. Another approach to
  mitigate pileup involves taking two transient measurements, one with and one
  without laser illumination, and using their difference to approximate the
  backgrond-free transient.}

  %Note
  % that this calculation involves only on the signal-to-background photon ratio,
  % which is independent of the actual number of counts recorded per exposure. In
  % other words, pileup and laser energy concerns may 
  % be addressed entirely independently. As for acquisition time, at a 10 MHz
  % pulse rate with
  % a 5\% photon detection rate, it takes just two seconds to acquire a million
  % photon events.}

% Furthermore, our system uses a SPAD and is therefore susceptible to pileup.
% Because the SPAD must be quenched before it can
% detect another photon, earlier photons
% from closer objects may systematically prevent detection of photons from further
% objects, causing strong distortion of the transient. Fortunately, at the expense of
% longer acquisition times, pileup can be mitigated
% to a large extent by operating in the low-flux regime
% where the number of photon events per second is controlled to be at most 5\% the
% number of laser pulses per second~\cite{oconnortcspc}. Finally, even in
% the high-flux regime, it is sometimes possible to correct pileup computationally~\cite{Heide:2018}.}

% While our prototype shows results for scanned/summed measurements, our scanning prototype operates in the low-flux regime,
% avoiding pileup. A hypothetical diffused SPAD prototype could also operate in
% this low-flux regime, which would yield identical measurement models and identical
% results. Figure~\ref{fig:hardware}(b)-(c) empirically shows that collecting and summing scanned
% measurements is nearly identical to capturing diffused measurements. ?!We show
% empirical comparisons between the two modes on a more complex scene in the supplement?!}

% Even if diffused and scanned/summed measurements are equivalent
%   computationally, they are not equivalent energetically.  This number is dependent on scene albedo, but all time-of-flight imaging
% systems share this dependency.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Future Work}
\edit{DELETE While our hardware prototype is large, future work could miniaturize this
system.} Our algorithm or similar sensor fusion algorithms could
\edit{DELETE also} be integrated into electronics that already contain the required hardware
components, for example, existing cell phones with single-pixel SPAD
proximity sensors and RGB cameras \edit{The small baseline of such sensors
  would also mitigate the effects of shading and complex BRDFs. Necessary
  adjustments, such as pairing near-infrared (NIR) SPADs with NIR sensors,
  could be made. More sophisticated intrinsic imaging techniques could also be
  employed, replacing the primitive RGB channel method described here.}

### 2020-07-09 paper/eccv2020CR/sections/hardware.tex
Added eccv2020 camera-ready draft.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Prototype RGB-SPAD Camera Hardware}

% The laser operates at 450~nm with a pulse repetition rate of 25~MHz with a peak power of 450~mW and average power of 0.5~mW.
% \begin{figure}[t]
% 	\centering
%   \includegraphics[width=0.5\columnwidth]{prototype_single_col.pdf}
%   \caption{Prototype scanning setup. The pulsed light from the laser travels
%     through a beam splitter before being guided by the galvo to the scene.
%     Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
%     camera is used to capture the image used to generate the monocular depth estimate
%     (the depth camera is not used).}
%   \label{fig:prototype}
%   % \vspace{-0.5em}
% \end{figure}

As shown in Figure~\ref{fig:hardware}, our prototype comprises a color camera
(Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM
series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis
galvanometer mirror system (Thorlabs GVS012). The laser operates at 670~nm with
a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power
of 0.5~mW. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single transient is generated by summing all of these measurements for a specific
scene. This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by
comparing it with the captured depth. To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD (see Figure~\ref{fig:hardware}(b,c)), we set up a slightly modified version of our prototype consisting of both scanned and optically diffused SPADs side-by-side. Additional details about the hardware prototype can be found in the supplement.

% show this in supplement
%The monocular depth estimate is calculated using the RGB image captured by the Kinect v2. The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps. The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth maps with an accuracy of about 1~cm. A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene. This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth---\edit{such validation would not be possible if we were to capture measurements with an optically diffused SPAD.}

% show this in supplement
%\edit{To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side. Details about this system can be found in the supplement. We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from the scanned SPAD are shown alongside the optically diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c). These results demonstrate that the two systems produce near equivalent measurements. Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions. That is, they observe scene from slightly different perspectives.}
	%NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?} \edit{We show proof-of-concept results captured by this system in   Figure~\ref{fig:captured_diffuse_small}. For}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental Results}
\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured.pdf}
	\caption{Experimental results. For each scene, we record a ground truth depth
    map that is raster-scanned with the SPAD (upper left subimages), and an RGB
    image (lower left). A monocular depth CNN predicts an initial depth map (top
    middle), which is corrected with the digitally aggregated SPAD histogram using the
    proposed method (top right), as shown by the error maps and root mean
    squared error (RMSE) for each example (lower center, right). The CNN is
    confused when we show it a photograph of a poster (bottom scene); it
    incorrectly predicts the depth of the scene depicted on the flat print. Our
    method is able to correct this error.}
	\label{fig:results_captured}
\end{figure}

>>>>

\subsection{Prototype RGB-SPAD Camera Hardware}
As shown in Figure~\ref{fig:hardware}, our prototype comprises a color camera
(Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM
series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis
galvanometer mirror system (Thorlabs GVS012). The laser operates at 670~nm with
a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power
of 0.5~mW. The ground truth depth map is raster-scanned at a resolution of
$512 \times 512$ pixels, and the single transient is generated by summing all of
these measurements for a specific scene. This allows us to validate the accuracy
of the proposed histogram matching algorithm, which only uses the integrated
single histogram, by comparing it with the captured depth. To verify that our
digitally aggregated scanned SPAD measurements match measurements produced by an
optically diffused SPAD (see Figure~\ref{fig:hardware}(b,c)), we set up a
slightly modified version of our prototype consisting of both scanned and
optically diffused SPADs side-by-side. Additional details about the hardware
prototype can be found in the supplement.

% show this in supplement
%The monocular depth estimate is calculated using the RGB image captured by the Kinect v2. The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps. The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth maps with an accuracy of about 1~cm. A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene. This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth---such validation would not be possible if we were to capture measurements with an optically diffused SPAD.

% show this in supplement
%To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side. Details about this system can be found in the supplement. We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from the scanned SPAD are shown alongside the optically diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c). These results demonstrate that the two systems produce near equivalent measurements. Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions. That is, they observe scene from slightly different perspectives.
	%NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?} We show proof-of-concept results captured by this system in   Figure~\ref{fig:captured_diffuse_small}. For

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental Results}
\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured.pdf}
	\caption{\edit{Experimental results. For each scene, we record a ground truth depth
    map that is raster-scanned with the SPAD (upper left subimages), and an RGB
    image (upper right subimages). A monocular depth CNN predicts an initial depth map (top
    middle left subimages), which is corrected with the digitally aggregated SPAD histogram using the
    proposed method (bottom left subimages), as shown by the error maps and root mean
    squared error (RMSE) for each example (middle left, bottom subimages). The CNN is
    confused when we show it a photograph of a poster (rightmost scene); it
    incorrectly predicts the depth of the scene depicted on the flat print. Our
    method is able to correct this error.}}
	\label{fig:results_captured}
\end{figure}

### 2020-07-09 paper/eccv2020CR/sections/introduction.tex
Added eccv2020 camera-ready draft.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{teaser_eccv.pdf}
  \caption{Monocular depth estimation predicts a depth map (second from right) from a
    single RGB image (second from left). The ill-posedness of the problem prevents
    reliable absolute depth estimation, resulting in large errors (inset images).
    The proposed method uses a \edit{single transient measurement aggregating
      the time-of-flight information of the entire scene (leftmost)} to correct
    the output of the depth estimation and optimize the quality of the
    estimated absolute depth (rightmost).}
  \label{fig:teaser}
\end{figure}

Traditional depth sensing techniques include those based on stereo or multiview,
active illumination, camera motion, or focus cues~\cite{szeliski2010computer}.
However, each of these techniques has aspects that may make their deployment
challenging \edit{in certain scenarios}. For example, stereo or multiview techniques require multiple
cameras, active illumination techniques may have limited resolution or require
time-consuming scanning procedures, and other techniques require camera motion
or multiple exposures at different focus distances.

One of the most promising approaches to overcoming these challenges is monocular
depth estimation (MDE), which requires only a single RGB image from a
conventional camera to recover a dense depth
map~\cite{Alhashim2018,Eigen2014,Fu2018,Laina2016,Saxena2006}. Recent approaches
to MDE employ neural networks that learn to predict depth by exploiting
\edit{pictorial depth} cues such as perspective, occlusion, shading, and relative
object size. While such models have significantly improved over recent years,
MDE approaches to date are incapable of reliably estimating absolute distances
in a scene due to the inherent scale ambiguities of monocular image cues.
Instead, these models excel in predicting ordinal depth, or the relative
ordering of objects in a scene~\cite{Eigen2014,Fu2018}. Interestingly, Alhashim
and Wonka~\cite{Alhashim2018} recently showed that if the median ground truth
depth of the scene is known, the initial output of a MDE network can be
corrected to produce accurate absolute depth.

@@

Although access to the median ground truth depth is impossible in a realistic
scenario, low-cost sensors capable of capturing aggregated depth information
from a scene are readily available. For example, the proximity sensor on recent
generation Apple iPhones uses a low-power pulsed light source and a
single-pixel \edit{time-resolved detector} %, single-photon avalanche diode (SPAD) 
to sense distance to an
object directly in front of the phone. %SPADs 
\edit{
Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon
avalanche diodes (SPADs), can measure the full waveform of time-resolved incident
radiance at each pixel (Fig.~\ref{fig:teaser}). These detectors form the
backbone of modern LiDAR
systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However,
single-photon sensor arrays} have
not yet been used for 3D imaging on consumer electronics, primarily because the requirement for
ultra-fast timing electronics makes it difficult to produce high-resolution
arrays at low cost and because the scanning requirement for single-pixel
systems introduces a point of mechanical failure and complicates
high-resolution, high-framerate imaging.

@@

Here, we propose to use a single-pixel \edit{time-resolved detector} and pulsed light source in an
unconventional way: rather than optically focusing them to record the distance
to a single scene point, we diffuse the emitted light and \edit{aggregate the reflected light over the
entire scene with the detector}. The resulting \edit{transient} measurement
resembles a histogram of the scene depth and we demonstrate that this can be
used to achieve accurate absolute depth when combined with the estimate of
\edit{any monocular depth estimator in a post-processing step}
(Fig.~\ref{fig:teaser}).

@@

To this end, we develop a sensor fusion strategy that processes the ordinal
depth computed by a monocular depth estimator to be consistent with the
measurements captured by the \edit{aggregated time-resolved} detector. We demonstrate in extensive
simulations that our approach achieves substantial improvements in the quality
of the estimated depth maps, regardless of which specific depth estimator is
used. \edit{Moreover, we build a camera prototype that combines an RGB camera and a single-pixel time-resolved detector and use it to validate the proposed depth estimation technique.} % With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware.

In summary, we make the
following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth histogram aggregated by a time-resolved detector to address scale ambiguity in MDE.	
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
	\item We build a prototype camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types. 
\end{itemize}

%\edit{\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single optically diffused measurement. The benefit of this approach is access to ground truth depth, allowing us to evaluate the efficacy of our method with measured data. However, when operating SPADs in certain conditions, they may observe a nonlinear aggregation effect known as pileup. In these conditions, the aggregated measurements may differ from a single optically diffused measurement. Yet, we experimentally verify that digitally and optically aggregated measurements captured with our system are very similar and pileup could also be computationally corrected~\cite{Heide:2018,Rapp:2019}, although we did not attempt this.}

%\edit{Our method is not without limitations. It still requires a laser and single-pixel LiDAR detector and is sensitive to ambient photons, which limit the maximum range. Being a variant of histogram matching, our method is not able to resolve ordinal depth errors (errors where an object is wrongly placed closer or farther relative to another object). In spite of these limitations, we find that our method performs remarkably well in practice.}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{teaser_eccv.pdf}
  \caption{Monocular depth estimation predicts a depth map (second from right) from a
    single RGB image (second from left). The ill-posedness of the problem prevents
    reliable absolute depth estimation, resulting in large errors (inset images).
    The proposed method uses a single transient measurement aggregating
      the time-of-flight information of the entire scene (leftmost) to correct
    the output of the depth estimation and optimize the quality of the
    estimated absolute depth (rightmost).}
  \label{fig:teaser}
\end{figure}

Traditional depth sensing techniques include those based on stereo or multiview,
active illumination, camera motion, or focus cues~\cite{szeliski2010computer}.
However, each of these techniques has aspects that may make their deployment
challenging in certain scenarios. For example, stereo or multiview techniques require multiple
cameras, active illumination techniques may have limited resolution or require
time-consuming scanning procedures, and other techniques require camera motion
or multiple exposures at different focus distances.

One of the most promising approaches to overcoming these challenges is monocular
depth estimation (MDE), which requires only a single RGB image from a
conventional camera to recover a dense depth
map~\cite{Alhashim2018,Eigen2014,Fu2018,Laina2016,Saxena2006}. Recent approaches
to MDE employ neural networks that learn to predict depth by exploiting
pictorial depth cues such as perspective, occlusion, shading, and relative
object size. While such models have significantly improved over recent years,
MDE approaches to date are incapable of reliably estimating absolute distances
in a scene due to the inherent scale ambiguities of monocular image cues.
Instead, these models excel in predicting ordinal depth, or the relative
ordering of objects in a scene~\cite{Eigen2014,Fu2018}. Interestingly, Alhashim
and Wonka~\cite{Alhashim2018} recently showed that if the median ground truth
depth of the scene is known, the initial output of a MDE network can be
corrected to produce accurate absolute depth.

@@

Although access to the median ground truth depth is impossible in a realistic
scenario, low-cost sensors capable of capturing aggregated depth information
from a scene are readily available. For example, the proximity sensor on recent
generation Apple iPhones uses a low-power pulsed light source and a
single-pixel time-resolved detector %, single-photon avalanche diode (
to sense distance to an
object directly in front of the phone. %SPADs 
Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon
avalanche diodes (SPADs), can measure the full waveform of time-resolved incident
radiance at each pixel (Fig.~\ref{fig:teaser}). These detectors form the
backbone of modern LiDAR
systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However,
single-photon sensor arrays have
not yet been used for 3D imaging on consumer electronics, primarily because the requirement for
ultra-fast timing electronics makes it difficult to produce high-resolution
arrays at low cost and because the scanning requirement for single-pixel
systems introduces a point of mechanical failure and complicates
high-resolution, high-framerate imaging.

@@

Here, we propose to use a single-pixel time-resolved detector and pulsed light
source in an unconventional way: rather than optically focusing them to record
the distance to a single scene point, we diffuse the emitted light and aggregate
the reflected light over the entire scene with the detector. \edit{The resulting
transient measurement resembles a histogram of the scene and can be used to
achieve accurate absolute depth in conjunction with a monocular depth estimate}
(Fig.~\ref{fig:teaser}).

@@

To this end, we develop a sensor fusion strategy that processes the ordinal
depth computed by a monocular depth estimator to be consistent with the
measurements captured by the aggregated time-resolved detector. We demonstrate in extensive
simulations that our approach achieves substantial improvements in the quality
of the estimated depth maps, regardless of which specific depth estimator is
used. Moreover, we build a camera prototype that combines an RGB camera and a single-pixel time-resolved detector and use it to validate the proposed depth estimation technique. % With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware.

In summary, we make the following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth transient
    aggregated by a time-resolved detector to address scale ambiguity in MDE.
  \item \edit{We introduce a depth reconstruction algorithm that uses the
    detector's image formation model in conjunction with a modified version of
    histogram matching, to produce a depth map from a single RGB image and
    transient. The algorithm can be applied instantly to any existing and
    future MDE algorithms.}
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset
    and demonstrate that our approach is able to resolve scale ambiguity while
    being fast and easy to implement.
	\item We build a prototype camera and evaluate its efficacy on captured data,
    assessing both the quality and the ability of our method to help
    generalization of monocular depth estimators across scene types.
\end{itemize}

%\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single optically diffused measurement. The benefit of this approach is access to ground truth depth, allowing us to evaluate the efficacy of our method with measured data. However, when operating SPADs in certain conditions, they may observe a nonlinear aggregation effect known as pileup. In these conditions, the aggregated measurements may differ from a single optically diffused measurement. Yet, we experimentally verify that digitally and optically aggregated measurements captured with our system are very similar and pileup could also be computationally corrected~\cite{Heide:2018,Rapp:2019}, although we did not attempt this.

%Our method is not without limitations. It still requires a laser and single-pixel LiDAR detector and is sensitive to ambient photons, which limit the maximum range. Being a variant of histogram matching, our method is not able to resolve ordinal depth errors (errors where an object is wrongly placed closer or farther relative to another object). In spite of these limitations, we find that our method performs remarkably well in practice.
